### 2020-07-28 draft.Rmd
remove commented code

```{r Tukey-HSD-setup}
# Helper functions
# comp_sum = function(val, t1){
# # Helper function for Mann-Whitney stat
#   full = sum(t1 < val)
#   partial = 0.5 * sum(t1 == val)
#   return(full+partial)
# }
# 
# mw_stat = function(t1, t2){
#   #Mann-Whitney statistic for two treatments
#   comp_sums = mapply(comp_sum, t2, MoreArgs = list(t1=t1))
#   return(sum(comp_sums))
# }
# 
# 
# general_stat_perm= function(full_data, n_s, stat_func){
#   # stat_func should take in a list of 
#   dataset = list()
#   k = length(n_s)
#   start=1
#   end=0
#   for (i in 1:k){
#     end = end + n_s[i]
#     dataset[[i]] = full_data[start:end]
#     start = end + 1
#   }
#   return(stat_func(dataset))
# }
# 
# calculate_critical = function(stat_dist, alpha){
#   # stat_dist is sorted
#   R = length(stat_dist)
#   init_crit = stat_dist[R*alpha]
#   if(sum(sample_q >= init_crit)/R == alpha){
#     return(init_crit)
#   }
#   index = sum(sample_q > init_crit)
#   return(sample_q[index])
# }

@@

# Permutation Tukey HSD test
# q_star = function(dataset){
#   # Permutation HSD pg 97
#   # Use the Mann-Whitney for T
#   k = length(dataset)
#   max_t = 0
#   for (i in 1:(k-1)) {
#     for(j in (i+1):k){
#       t = abs(mw_stat(dataset[[i]], dataset[[j]]))
#       if (t > max_t){
#         max_t = t
#       }
#     }
#   }
#   return(max_t)
# }

@@

k = length(treat_list)
n_s = mapply(length, treat_list)
N = sum(n_s)
full_data = unlist(treat_list)

@@

# R = 10000
# permutations = matrix(NA, ncol = N, nrow=R)
# for (i in 1:R){
#   permutations[i,] = sample(full_data)
# }
# sample_q = apply(permutations, 1, general_stat_perm, n_s, q_star)
# sample_q = sort(sample_q, decreasing = TRUE)
# 
# 
# 
# crit_alpha = calculate_critical(sample_q, alpha)
# crit_adj = calculate_critical(sample_q, adjusted_alpha)
# # crit_message = sprintf("critical values of significance levels %s and %s are %s and %s respectively", alpha, adjusted_alpha, crit_alpha, crit_adj)
# # print(crit_message)
# 
# q_obs = q_star(treat_list)
# obs_message = sprintf("The observed value of Q* is: %s", q_obs)
# print(obs_message)
# 
# counts = sum(sample_q>= q_obs)
# p_val = counts/R
# p_message = sprintf("With a p-value of %s", p_val)
# print(p_message)
kw_result = kruskal.test(treat_list)
kw_result

>>>>

@@

@@

k = length(treat_list)

@@

kw_result = kruskal.test(treat_list)
kw_result
